\textsf{Are large language models superhuman chemists?}

### 2024-03-25 src/tex/ms.tex

    However, we still have only very limited systematic understanding of the chemical reasoning capabilities of LLMs, which would be required to improve models and mitigate potential harms. 
    Here, we introduce \enquote{\chembench}, an automated framework designed to rigorously evaluate the chemical knowledge and reasoning abilities of state-of-the-art LLMs against the expertise of human chemists.

>>>>

    However, we still have only very limited systematic understanding of the chemical reasoning capabilities of LLMs, which would be required to improve models and mitigate potential harms. 
    Here, we introduce \enquote{\chembench,} an automated framework designed to rigorously evaluate the chemical knowledge and reasoning abilities of state-of-the-art LLMs against the expertise of human chemists.
